### 2021-02-13 main.tex
par poznamek
Clean up some todos
Add some todos

\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient}

@@

>>>>

\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient, epoch}

@@

\todo{Describe problem again, this time precisely / technically.}
\todo{Prove that minimizing precedence cost corresponds to sorting by symbol cost.}
\todo{Advantage of using pairs of precedences: we need to solve classification rather than regression.}
\todo{Intuice: snazime se nastavit costy tak, aby co nejvic dvojic dopadlo spravne.}
\todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}
\todo{Compare our GCN to Michael, Mirek etc.}
